---
title: "Shiny presentation"
author: "Rajeev Kumar"
date: "May 22, 2018"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Executive Summary

This R Markdown presentation provides insight into the variation of mpg v/s weight based on the type of cylinder of the vehicle. Looking at the interactive plot we can identify that weight has slighly different impact on the mpg for different number of cylinders.



## Code of generating interactive plot
library(shiny)
inputPanel(
  sliderInput("cyl1", "Number of cylinders:",min=4, max = 8, value = 6,step=2)
  
 )
model_l<-  reactive({
    mtcars1<-mtcars[mtcars$cyl==input$cyl1,]
    abline(lm(mpg~wt,data=mtcars1), col="red")
  })

renderPlot({
    # draw the scatter plot
    mtcars1<-mtcars[mtcars$cyl==input$cyl1,]
    plot(mtcars1$wt, mtcars1$mpg, type="p",main="Scatterplot mpg v/s car weight",
         xlab="Car Weight ", ylab="Miles Per Gallon ", pch=19)
    #call function to draw abline.
    model_l()

  })


## 

```{r eruptions,echo=FALSE}
library(shiny)
inputPanel(
  sliderInput("cyl1", "Number of cylinders:",min=4, max = 8, value = 6,step=2)
  
 )
model_l<-  reactive({
    mtcars1<-mtcars[mtcars$cyl==input$cyl1,]
    abline(lm(mpg~wt,data=mtcars1), col="red")
  })

renderPlot({
    # draw the scatter plot
    mtcars1<-mtcars[mtcars$cyl==input$cyl1,]
    plot(mtcars1$wt, mtcars1$mpg, type="p",main="Scatterplot mpg v/s car weight",
         xlab="Car Weight ", ylab="Miles Per Gallon ", pch=19)
    #call function to draw abline.
    model_l()

  })

```
